% #############################################################################
% Acknowledgments
% !TEX root = ../main.tex
% #############################################################################

Foremost, I would like to express my sincere gratitude to my supervisors Dr. Diogo Caetano and Prof. Gonçalo Tavares for their guidance, knowledge and time invested in this project. Aside from the opportunity of working in INESC with a pleasant research team.

I wish to extend my heartfelt thanks to Eng. Ruben Afonso and Eng. Fabian Näf, two extraordinary Ph.D. students whose unwavering support and invaluable assistance lead to the completion of this thesis. Their expertise, guidance, and patience have been truly exceptional. They generously shared their knowledge, provided insightful feedback, and dedicated countless hours to helping me.

To Ricardo Lorena, a fellow master's student, deserves my appreciation for his help in the completion of my thesis. Throughout our individual research projects, I had the privilege of exchanging valuable ideas and collaborating closely with Ricardo.

I thank all my family for their friendship, encouragement and caring over these years. They were always there for me through thick and thin, and without whom this project would not have been possible. Special thanks to my parents, who always believed in me even when I didn't. My mother, Marta Rafael, for the wise counsel, sympathetic ears and all the help throughout my academic path. My father, João Rafael, for the strong economically support and for showing me how hard work, consistency, and dedication are fundamental traits for any human.

To Carolina Guerra, my wonderful girlfriend, who would do everything in her power to make me feel happy, even when she was not feeling so well. During all the stress involved in this dissertation, she was always there with kind and reassuring words.

I thank my fellow friends, João Faustino and Diogo Bernardo, for the stimulating discussions, for the sleepless nights we were working together before deadlines, and for all the fun we had in the last five years. To all the friends I have met that led to this point in my life.

Lastly, throughout the development of this dissertation, I have received a great deal of support and assistance. I would like to thank and apologize to all the people that I have left outside of this acknowledgement.

\begin{flushright}
Thank you. To each and every one of you -- Thank you.
\end{flushright}


